%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                      Homework 1                            %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letter]{article}

\usepackage{lipsum}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1.5in]{geometry}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{framed} 
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{titling}
\usepackage{fancyhdr}

\pagestyle{fancy}


\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\newenvironment{menumerate}{%
  \edef\backupindent{\the\parindent}%
  \enumerate%
  \setlength{\parindent}{\backupindent}%
}{\endenumerate}







%%%%%%%%%%%%%%%
%% DOC INFO %%%
%%%%%%%%%%%%%%%
\newcommand{\bHWN}{1}
\newcommand{\bCLASS}{MATH H104}

\title{\bCLASS: Homework \bHWN}
\author{William Guss\\26793499\\wguss@berkeley.edu}

\fancyhead[L]{\bCLASS}
\fancyhead[CO]{Homework \bHWN}
\fancyhead[CE]{GUSS}
\fancyhead[R]{\thepage}
\fancyfoot[LR]{}
\fancyfoot[C]{}
\usepackage{csquotes}

%%%%%%%%%%%%%%

\begin{document}
\maketitle
\thispagestyle{empty}


%%%%%%% Be sure to set the counter and use menumerate
\section{Real Numbers}

\begin{menumerate}
	\setcounter{enumi}{2}
	\item Recast the following English sentences in mathematics, using correct mathematical grammar. Preserve their meaning.
		\begin{menumerate}
			\item \textit{2 is the smallest prime number.} Let $P \subset \mathbb{N}$ denote the set of prime numbers.
			Consider that $t = 2$ is clearly a member of P.
			Then for all $p \in P$, $t \leq P$.

			\item \textit{The area of any bounded plane region is bisected by some line parallel to $x$-axis.} 

			Before we claim the above we must first rigorize the notion of a bounded plane region. The following uses a notion of open and closed sets in $\mathbb{R}^2$.

			\begin{definition}
				 We say that $B_r(x_0)$ is an open ball of radius $r>0$ if and only if
				 $$B_r(x_0) = \{ x \in \mathbb{R}^2 \ |\ \|x - x_0 \| < r \}.$$
				 Furthermore $\bar{B}_r(x_0)$ is a closed ball of radius $r>0$ if and only if
				 $$\bar{B}_r(x_0) = \{ x \in \mathbb{R}^2 \ |\ \|x - x_0 \| \leq r \}.$$
			 \end{definition} 
 			 Using the above definition we now give our notion of a bounded plane reigon. 
 			 \begin{definition}
 			 	If $A$ is a subset of $\mathbb{R}^2$ we will say that $A$ is the area of a bounded plane region if and only if for every $x \in A$, there is an open or closed ball centered at $x$ which is a subset of $A.$
 			 \end{definition}
 			 Lastly, we give the notion of a parallel line to the $x$-axis
 			 \begin{definition}
 			 	We say that $L_r \subset \mathbb{R}^2$ is a line parallel to the $x$-axis at radius $r$ if and only if 
 			 		$$L_r = \{ (x,y) \in \mathbb{R}\ | \ y = r \}.$$ 
 			 \end{definition}
			 
			 Now it is simple to propose the theorem of symantic equivalence to the question.

			 \begin{theorem}
			 Let $A$ be the area of a bounded plane region in $\mathbb{R}^2$. Then, there exists some line parallel to the $x$-axis of height $r$, $L_r$, such that $L_r \cap A \neq \emptyset$ and both
			 	\begin{equation}
			 			A_L = \{ (x,y) \in A\ |\ y < r \}\ \mathrm{and}\ 
			 			A_U = \{ (x,y) \in A\ |\ y \geq r\}
	 			\end{equation}	
	 		are areas of bounded plane regions.

 			 \end{theorem}

 			 \item \textit{"All that glitters is mot gold."}  Let $G$ be the set of all object which glitter. Then let $A$ be the set of all gold objects. $A\neq G$.

		\end{menumerate} 

	\setcounter{enumi}{11}
	\item \textit{Prove the following.}
		 \begin{theorem}
			There exists no smallest positive real number.
		\end{theorem}
		\begin{proof}
		 Suppose that there exists a smallest real number, say $a \in \mathbb{R}$. Clearly $a >0$ and so is $\frac{a}{2}$. Furthermore $\frac{a}{2} < a,$  and hence we reach a contradiciton. Therefore does not exist a smallest postivie real number.
		\end{proof}
		\begin{theorem}
			There exist no smallest positive rational number. 
		\end{theorem}
		\begin{proof}
			 Suppose that there exists a smallest rational number, say $q \in \mathbb{Q}$. Clearly $q >0$ and so is $\frac{q}{2}$. Furthermore $\frac{q}{2} < q,$  and hence we reach a contradiciton. Therefore does not exist a smallest postivie rational number.
		\end{proof}

		\begin{theorem}
			Let $x \in \mathbb{R}.$ Then there does not exist a smallest real number $y$ such that $y > x$.
		\end{theorem}
		\begin{proof}
			Suppose that such a $y$ exists. Now consider $\frac{x+y}{2}= b$. Clearly $b > x$, and remarkably $b < y$. Hence $y$ is not the smallest real number such that $y > x$. This leads to a contradiction, and therefore there is no smallest $y$ satisfying the conditions.
			
		\end{proof}

	\setcounter{enumi}{21}
	\item \textit{Show the following.} 
		\begin{menumerate}
			\item \textit{Fixed points}: \begin{theorem}
				The function $f: A \to A$ has a fixed point if and only if the graph of $f$ interesects the diagonal.
			\end{theorem}
			\begin{proof}
				We first show the right implication. If $f$ has a fixed point, then there is some $a \in A$ such that $f(a) = a$. Now consider the graph of $f$, 
				$$f(A) = \{(a, f(a) \in A\}.$$ 
				Since $f$ has a fixed point, $f(A)$ contains $(a,a).$ Hence the intersection of $f(A)$ with the diagonal of $A\times A$,$D,$ must contain $(a,a)$ at the least and hence is nonempty.

				On the otherhand if the graph of $f$ intersects the diagonal, then there exists some $(a,a) \in D$ such that $(a,a) \in f(A).$ Then by definition of the graph of $f$, $(a,a) = (a,f(a))$, which implies that $f(a) = a.$ This completes the proof.
			\end{proof}


			\item \textit{Intermediate fixed point}
			\begin{theorem}
				Every continuous function $f: [0,1] \to [0,1]$ has at least one fixed-point.
			\end{theorem}
			\begin{proof}
				To show this we recall the intermediate value theorem. More specifically we want to find a function whose $0$ exists on $[0,1]$ which implies the theorem. Consider that $f(x) =x$ implies that $0 = f(x) - x$, so let's simply let $q(x) = f(x) - x$. By definition of the bound on the codomain, $g(0) \geq 0$ and $g(1) \leq 0$. Then application of the intermediate value theorem yields that there exists at $c \in [0,1]$ with $g(c) = 0.$ Hence, $f(a) = a$. This completes the proof.
			\end{proof}
			\item No, consider the case of some function for which $f(x) > x$ on $(0,1)$. Such a function need not attain the value $f(0) = 0, f(1) = 1$ because such values could not possiblt exist on its graph. Hence, $f(x) \neq x$ for all $x$. 
			\item No, consider the function $f(x) = x+0.5$ when $0\leq x < 0.5$, and $f(x) = x-0.5$ when $0.5 \leq x \leq 1$. This function never is equivalent to $g(x) = x.$
		\end{menumerate}

	\item \textit{Show the following.} 
		\begin{menumerate}
			\item \textit{Dyadic squares:}
				\begin{theorem}
					 If $x$ and $y$ are two dyadic squares, then they are either identical, intersect along a common edge, intersect at a common vertex, or do not intersect at all.
				\end{theorem}
				\begin{proof}
					Since we must show all cases, let us consider them with respect to the general definition of a planar dyadic cube. In particular, $x,y \in \mathbb{Q}_2^2.$ Let us fix $x$ such that
					$$x = \left[\frac{p}{2^k}, \frac{p+1}{2^k}\right]^2 \mathrm{and}\ y = \left[\frac{q}{2^k}, \frac{q+1}{2^k}\right]^2$$
					for some $p, k, q \in \mathbb{Z}.$

					If $q = p$, then $y = x$ naturaly. In the case that $q > p+1$ or $q+1 < p$, we have that $x \cap y = \emptyset$. Next consider intersections along different edges. If
					 $$y = \left[\frac{p}{2^k}, \frac{p+1}{2^k}\right]\times \left[\frac{p+1}{2^k}, \frac{p+2}{2^k}\right],$$
					 then $y \cap x = [(\frac{p}{2^k}\frac{p+1}{2^k}), (\frac{p+1}{2^k},\frac{p+1}{2^k})]$. In general, 
					 $$y = \left[\frac{p+r}{2^k}, \frac{p+r+1}{2^k}\right]\times \left[\frac{p+s}{2^k}, \frac{p+s+1}{2^k}\right]$$
					 implies the following intersections.

					 If $r = 1, s = 0$, then $x \cap y = \left[(\frac{p+1}{2^k},\frac{p}{2^k}),(\frac{p+1}{2^k}, \frac{p+1}{2^k})\right]$. If $r = -1, s= 0$, then  $x \cap y = \left[(\frac{p}{2^k},\frac{p}{2^k}),(\frac{p}{2^k}, \frac{p+1}{2^k})\right].$ If $r= 0, s = 1$, then  $x \cap y = \left[(\frac{p}{2^k},\frac{p+1}{2^k}),(\frac{p+1}{2^k}, \frac{p+1}{2^k})\right]$. If $r=0,s=-1,$ then  $x \cap y = \left[(\frac{p}{2^k},\frac{p}{2^k}),(\frac{p+1}{2^k}, \frac{p}{2^k})\right]$.

					 Lastly we need to consider the vertex edge cases. If $r =1, s= 1$, then $x \cap y = \{(\frac{p+1}{2^k},\frac{p+1}{2^k})\}$. If $r =-1, s= 1$, then $x \cap y = \{(\frac{p}{2^k},\frac{p+1}{2^k})\}$. If $r =-1, s= -1$, then $x \cap y = \{(\frac{p}{2^k},\frac{p}{2^k})\}$. If $r =1, s= -1$, then $x \cap y = \{(\frac{p+1}{2^k},\frac{p}{2^k})\}$.  

					 Furthermore if $r$ and $s$ attain other values, we have those cases previously considered. Hence the proof is complete.

 				\end{proof}

 			\item \textit{For the following problem we adopt the following notation.}
 				\begin{definition}
 				 We say that say that some $X \subset \mathbb{R}^n$ is a dyadic hyper-interval of partition $2^{-\gamma}$ if and only if 
 				 $$X \in \overline{\Delta_n^k} = \left\{ Y \subset \mathbb{R}^n\ |\ Y = \bigtimes_{i\in\delta_k}2^{-\gamma}\left[(m_1,\dots,m_n),(m_1 , \dots,m_i +1,\dots, m_n)\right]\right\}, $$
 				 where $\delta_k$ is the index set of dimensions in which the interval is non-empty and non-singular. Furthermore, $|\delta_k| = k$, and $m_i \in \mathbb{Z}.$
 				\end{definition}
 					So now we need to operationalize this proof. If $x$ and $y$ are two dyadic squares, then they are either identical, intersect along a common edge, intersect at a common vertex, or do not intersect at all.
				\begin{theorem}
					  In other words, if $X,Y \in \overline{\Delta_n^n}$ are of the same partition, $2^{-\gamma}$, let
					   $$Y = \bigtimes_{i=1}^k2^{-\gamma}\left[(m_1 + r_1,\dots,m_n + r_n),(m_1 + r_1, \dots,m_i +1 + r_i,\dots, m_n + r_n)\right],$$ 
					   where the $m_j$ are those which define $X$, and $r_j \in \mathbb{Z}.$ Then, if $|r_j| \leq 1$ for all $j$, the following two results hold. If $k = n - \sum_i|r_i| > 0$,  $X \cap Y \in \overline{\Delta_n^k}$. If $k = 0$, $X \cap Y \subset \mathbb{Q}_2^n$ with $|X\cap Y| = 1$. Otherwise if there exists some $j$ such that $|r_j| > 1$, then $X \cap Y = \emptyset.$

				\end{theorem}
				\begin{proof}
					We denote $X_j, Y_j$ as the $j^\mathrm{th}$ interval composing $X$ and $Y$. In the above definition of $Y$ we wish to explore a multitude of different $r_j$ values so as to express the theorem.

					In the simplest case, $|r_j| > 1$ for some $j$ then $$y_j = 2^{-k}[(m_1 + r_1,\dots,m_j + r_j\dots,m_1+r_1),(m_1+r_1,\dots m_j+r_j+1,\dots,m_n+r_n)].$$ Clearly $m_j + 1 < m_j + r$ or $m_j  > m_j +r_j + 1$, and thus $y_j \cap x_j = \emptyset$, we have that the whole cartesian product, 
						$$X\cap Y = \emptyset \times \left(\bigtimes_{i\neq j}^n x_j\cap y_j\right) = \emptyset,$$ 
						because $\emptyset \times B$ cannot form any pair $(a,b)$ as there is no $a\in\emptyset.$

					We claim that when $|r_i| \leq 1 $, $X \cap Y\in \overline{\Delta_n^k}$ for $k = n - \sum_{i=1}^n|r_i| > 0.$ Let $(n_p)$ denote the finite (possibly empty) list of indices for which $|r_j| = 1.$ In other words, for all $p$, $|r_{n_p}| = 1,$ else $|r_j| = 0.$ The intersection as aforementioned is the cartesian product of all $x_j, y_j$. Hence for $j \notin \{n_p\}$,  $x_j \cap y_j \in \overline{\Delta_n^1}$ with $\delta_1 = {j}.$ Hence, the cartesian product of all such $j$ is $X^* \cap Y^* \in \overline{\Delta_n^c}$ with $\delta_{c} = \{j \neq n_p \forall p\},$ and $c= n-|\{n_p\}|.$ We claim that $X \cap Y$ cannot exist in any higher dimenisonality than $X^* \cap Y^*.$ 

					Suppose $X \cap Y \in \overline{\Delta_n^d},$ with $n \geq d > c$.  This implies that there exists a $q \in \{n_p\}$ such that $x_q \cap y_q = z_q$ is non-singular and non-empty. We have that
					\begin{equation*}
						\begin{aligned}
							z_q &= [(m_1,\dots,m_q,\dots,m_n), (m_1,\dots,m_q+1,\dots,m_n)]\\
								&\;\;\;\;\; \cap  [(m_1,\dots,m_q \pm 1,\dots,m_n), (m_1,\dots,m_q+1 \pm 1,\dots,m_n)] \\
								&= \left\{\left(m_1,\dots,m_q+\frac{1\pm1}{2},\dots,m_n  \right)\right\}
						\end{aligned}
					\end{equation*}
					is singular. Hence we reach a contradiction and $X\cap Y \in \overline{\Delta_n^c}. $

 				\end{proof}
		\end{menumerate} 


		\item \textit{Show the following}
			\begin{menumerate}
			\item \textit{Dyadic squares in the unit ball.}
				\begin{theorem}
				Given $\epsilon > 0,$ show that the unit disc contains finitely many dyadic squares whose total area exceeds $\pi - \epsilon,$ and which intersect with eachother only along their boundries.
				\end{theorem}

				\begin{proof}
				     Let $B_c^2$ be a disk of radius $\sqrt{\frac{\epsilon}{\pi}} \leq c < 1$. Then consider the finite set $S_k$ of all dyadic squares of partition $2^{-\gamma} = \frac{1 - c}{2}$ such that $B^2 \supset \bigcup S_k \supset B_c^2$. Clearly the area of $\bigcup S_k > \pi - \epsilon$ but less that $\pi.$ Hence for any $\epsilon > 0$, take $S_k$ as aforementioned, and these satisfying squares do not intersect. The proof is complete.
				\end{proof}

			\item \textit{Disjoint dyadic squares.}
				\begin{theorem}
				Given $\epsilon > 0,$ show that the unit disc contains finitely many dyadic squares whose total area exceeds $\pi - \epsilon,$ and which are disjoint.
				\end{theorem}

				\begin{proof}
				 	For any $\epsilon > 0,$ let $r = \frac{1+\sqrt{\frac{\epsilon}{\pi}}}{2}.$ Clearly such a point is the average radfius of the unit ball and the unit ball with radius $r.$ Now as before, divide the inside into pices of side length $2^{-n+1} = 1 - \sqrt{\frac{\epsilon}{\pi}}. $ If only every second square in every direction is selected, that set, say $S_1$, is clearly disjoint. Furthermore the total area of this set is at least $$a_1 = \frac{\alpha_0}{4} = \frac{\pi r^2}{4}.$$

				 	Now for those dyadics not selected, subdivide those sets into $8$ pieces in basis direction, and choose every other dyadic which is disjoint from $S_1$ and dyadics of the same class. Let $S_2$ be the set of $S_1$ union with this new set. The area of $S_2$ is at least  
				 	$$a_2 = a_1 + \frac{\alpha_0-a_1}{4}.$$

				 	Upon repeating this process we yield the following recurrence relation, $$a_n = a_{n-1} + \frac{\alpha_0-a_{n-1}}{4}.$$ Hence, we apply the methods of non-homogeneous recurrence relations and find that the general solution is clearly $a_n = c_1\left(\frac34\right)^n$. Then we solve for the particular solution, and yield that $a_n^p = \pi r^2.$ So we simply solve $a_1 = \frac{\alpha_0}{4}=c_1\frac34 + \alpha_0$ for $c_1.$ Upon yielding $c_1 = -\alpha_0$, we find the total solution to the area upon $n$ repitions of the process is 
				 	$$a_n = -\alpha_0\left(\frac34\right)^n + \alpha_0.$$

				 	Now we show that there exists an $N$ such that for some $n > N$, $a_n > \pi - \epsilon.$ Observe, \begin{equation}
				 		\begin{aligned}
				 			\alpha_0 - \alpha_0\left(\frac34\right)^n &< \pi - \epsilon \\
				 			 \left(\frac34\right)^n &> \frac{\epsilon-\pi}{\alpha_0} + 1 \\
				 			 	n \ln\left(\frac34\right) &> \ln\left(\frac{\epsilon-\pi}{\alpha_0} + 1\right).
				 		\end{aligned}
				 	\end{equation} Hence, let $N(\epsilon) = \frac{\ln\left(\frac{\epsilon-\pi}{\alpha_0} + 1\right)}{\ln\left(\frac34\right)} $. By the logic of derivation for $N,$ for every $\epsilon > 0$ and for all $n > N(\epsilon),$ $a_n > \pi - \epsilon.$ 

				 	Take the first such $n.$ Then the set of disjoint dyadics, $S_n$, which induce the area $a_n$ is finite, and the proof is complete.
				\end{proof}

				\item \textit{Dyadic hypercubes filling a ball.}
				\begin{theorem}
				Given $\epsilon > 0,$ show that the unit ball contains finitely many dyadic hypercubes whose total hypervolume exceeds $V_m(1) -\epsilon = \frac{\pi^{m/2}}{\Gamma(\frac{m}{2}+1)} - \epsilon,$ and which intersect with eachother only along their boundries.
				\end{theorem}

				\begin{proof}
				     Let $B_c^m$ be a ball of hypervolume $\epsilon < v < V_m(1),$ and therefore radius $\frac{\left(\epsilon\Gamma(\frac{m}{2} + 1)\right)^{1/m}}{\sqrt{\pi}} \leq c < 1$. Then consider the finite set $S_k \subset \overline{\Delta_m^m}$ of all dyadic hypercubes of partition $2^{-\gamma} = \frac{1 - c}{2}$ such that $B^m \supset \bigcup S_\gamma \supset B_c^m$. These cubes will fill the ball of radius $\frac{\left(\epsilon\Gamma(\frac{m}{2} + 1)\right)^{1/m}}{\sqrt{\pi}}$ at least. Clearly the hypervolume of $\bigcup S_k > V_m(1) - \epsilon$ but less than $V_m(1).$ Hence for any $\epsilon > 0$, take $S_\gamma$ as aforementioned, and these satisfying hypercubes do not intersect except along common edges (as proved in $23$. The proof is complete.
				\end{proof}


				\item \textit{Prove theorem 10 when the unit ball is replaced with the unit square, and circles are inscribed on the dyadic hypercube lattice.}
				\begin{proof}
					Given $\epsilon > 0.$ Let $B^2_{-\gamma/2}$ denote the disk inscribed in the dyadic square $\delta \in \overline{\Delta_2^2}$ of partition $2^{-\gamma}$ at some position in $\mathbb{Q}_2^2.$ Now consider the unit square and the square at the origin of area $\epsilon_2$ and sidelength $\sqrt{\epsilon}+c.$ Define $\gamma$ to be the rounded solution of $2^{-\gamma} = \frac{1- \sqrt{\epsilon}+c}{2}.$ Then let $S_1$ be the family of every other dyadic square of partition $2^{-\gamma}$ filling the square of area $\epsilon_2$ completeley and then some. The area of such squares is at least $a_1 = \frac{\epsilon_2}{4}. $ Then the area of union of the family of ball inscribing all dyadic squares in $S_1$ is $b_1 = \frac{\epsilon_2}{8}.$ 

					For those squares not selected subdivide them into $16$ dyadic squares and choose every other such that these squares are disjoint from one another and their family is disjoint from $S_1.$ Take the union of their family and $S_1$ to produce $S_2$ whose area is at least $a_2 = a_1 + \frac{\epsilon_2-a_1}{8}.$ Taking those circles inscribed yields that $b_2 = b_1 + \frac{\epsilon_2-a_1}{32}.$

					Repeating this process yields a geometric series $b_n$ similar to $a_n$ in part (b). By the same logic in part (b), there will exist an $n$ such that $b_n> \epsilon$ and hence a finite disjoint dyadic partitioning of the unit square such that the area of disk inscription of this partitioning has area greater than $\epsilon$ which approaches $\epsilon_2$. This completes the proof. 
				\end{proof}
			\end{menumerate}

		\setcounter{enumi}{31}
		\item \textit{Suppose that $E$ is a convex region in the plane bounded by a curve $C.$}
			\begin{menumerate}
				\item \textit{Show the following}
					\begin{theorem}
						The curve $C$ has a unique tangent line except at a countable number of points.
					\end{theorem}

					\begin{proof}
						We first show that their exists a tangent line for every point $c\in C.$ Let $$T_c = \left\{x\in\mathbb{R}^2\;|\;x=c+rt, t \in \mathbb{R}\right\}, $$ for some slope vector $r$ such that $T_c \cap (E\setminus C) = \emptyset.$ We show that $\forall c, T_c \cap E \neq \emptyset.$ 
						Take some $c \in C$ and fix it. Then for some sequence of points on the curve, $q_n$, which start at some other point $c'$ and increase monotonically with respect to angle from the center of $E$ such that $q_n \to c.$ Let the secant line to $c$ at some point $q$ be denoted, $$S_q = \left\{x \in \mathbb{R}^2\ |\ q + \frac{(c-q)}{\|c-q\|}t, t\in \mathbb{R}\right\}.$$
						Consider that $[q_n,c] \subset S_{q_n},$ and $ S_{q_n} \setminus {[q_n,c]} \cap E =\emptyset.$ For all $n$, $[q_n,c]$ is clearly non-empty (it contains at least, $c$), so $\bigcap_n[q_n,c]$ is also non-empty. Therefore, as $q_n \to c$, $S_{q_n} \to S_{c} \supset \bigcap_n S_{q_n} = {c}$. $S_c$ could not possibly contain an element of $E \setminus C.$ Suppose it contains, $e \in E \setminus C,$ for the purpose of reaching a contradiction. Then $e \in [c,c]$ such that $e\neq c,$ which leads to a contradiction. Therefore, $S_c = T_c$ for some tangent line satisfying the definition.

						Now we will show that $T_c$ is unique except at countably many points. Let us define the function $\tau : C \to [0,2\pi]$ which assigns to every point on the curve $C$ the angle of its tangent line ,with respect to some starting angle of a point $q\in C$. By the logic above, for every p $\tau(p)$ exists. Let $\phi:\mathbb{R}\to C$ be a bijective paramaterization of $C$ starting at some point $q$ such that one walks counter clockwise with respect to $q$ a distance $t$ and yields $\phi(t).$

						It is easy to see that $\phi(t)$ is a continuous function because the region $E$ is connected. We claim that $\tau \circ \phi (\mathbb{R})$ has countably many discontinuities. For every $p,$ $\tau(p)$ is the angle of the tangent to $p.$ If no angle exists, there must exist more than one tangent by the previous logic. Furthermore angle for which there is no tangent lies in some open interval. In other words, $\tau(\phi(S \subset \mathbb{R}))$ experiences discontinuities in disjoint intervals.

						Given a family of open disjoint intervals in $\mathbb{R}$, we claim that those disjoint families are countable. This holds because for each interval there exists a unique rational number therein, and since the rationals are countable, the family must be countable. Therefore, the discontinuities in  $\tau(\phi(S \subset \mathbb{R}))$ are countably many. Geometrically speaking, the points at which there exist no unique tangent in the convex curve $C$ surrounding a convex region $E$ are therefore countably many.

						This completes the proof.
					\end{proof} 

					\item\textit{Show the following.}
					\begin{theorem}
						If $f$ is a convex function, then it has a derivative except at countably many points.
					\end{theorem}

					\begin{proof}
						If $f$ is a convex function, then for any $x,y \in [a,b]=I$, $m = \min_I f$, $M= \max_I f$, the line segment $\overline{f(x),f(y)}$ is contained in the region $$S = \left\{(x,y)\in I \ |\ m \leq b \leq f(a)\right\}.$$ Let $C$ be the curve, $C = \{(x,f(x))\}_{x\in I} \cup [(a,m),(a,f(a))] \cup [(a,m),(b,m)] \cup [(b,m), (b,f(b))].$ Since $S$ is convex and bounded by $C$, $C$ has tangents everywhere except at countably many points. Since $G = \{(x,f(x))\}_{x\in I}\subset C$ then the graph $G$ has tangents except at countably many points. In other words, in any $[a,b]$, $f$ has derivatives at except at countably many points. The proof is complete.
					\end{proof}
			\end{menumerate} 

			\setcounter{enumi}{44}
				\item \textit{Let $(a_n)$ be a sequence of real numbers. It is bounded if the set $A = \{a_1, a_2, \dots \}$ is bounded. The limit supremum, or lim sup, of a bounded sequence $(a_n)$ as $n\to\infty$ is}
				$$\limsup_{n\to\infty }a_n = \lim_{n\to\infty}\left(\sup_{k\geq n} a_k\right)$$
				\begin{menumerate}
				\item \textit{Why does lim sup exist?} It exists because if $A$ is bounded, so is any subset. Therefore the set of $a_k$ with $k\geq n$ must be a bounded set in $\mathbb{R}$ with an upper bound $\sup_{k\geq n}{a_n}.$
				\item \textit{If $\sup{a_n} = \infty$, how should we define $\limsup_{n\to\infty}a_n$?}. One should define $\limsup a_n = \infty,$ as every subsequence diverges.
				\item \textit{If $\lim a_n = -\infty$, how should we define $\limsup_{n\to\infty}a_n$?}. One should define $\limsup a_n = -\infty,$ as every subsequence diverges.

			\item Prove the following.

				\begin{definition} We say $(s_{n})$ is a sequence of supremums for a sequence $(a_n)$ if and only if,$ s_n = \sup\{a_k : k \geq n\}.$
	 			\end{definition}
				\begin{theorem}
			    Let $\{a_n\}, \{b_n\}$ be sequences in $\mathbb{R}$. If $\limsup a_n$ and $\limsup b_n$ are finite, 
			    then $\limsup\left(a_n + b_n\right) \leq \limsup a_n + \limsup b_n$.
			    \end{theorem}
			    
			    \begin{proof}
			    Consider the sequences of supremums for both $a_n$ and $b_n$ respectively, $\{s_{a,k}\}, \{s_{b,k}\}$.
			    Also consider the sequence of supremums for $a_n + b_n$, that is $\{s_{c,k}\}$.
			    
			    
			    We have that for fixed $k$, $a_n + b_n \leq s_{a,k} +  s_{b,k}$ for all $n \geq k$ 
			    by adding the inequalities defined for $s_{a,k}$ and $s_{b,k}$.
			    
			    Then notice that $\sup_{n\geq k} a_n +b_n$ is less than or
			    equal to $  s_{a,k} + s_{b,k}$ for $k$ fixed. 
			    So
			    \begin{equation}
			    \sup s_{c,k} \leq  s_{a,k} +  s_{b,k}
			    \end{equation}
			    holds as $k\to \infty$. Therefore $\limsup{(a_n + b_n)} \leq \limsup{a_n} + \limsup{b_n}$.
			    This completes the proof.
			    \end{proof}
				\newpage
			\item \textit{Define the limit infinum and relate it to the limit supremum.}
				\begin{definition} We say $(i_{n})$ is a sequence of infinums for a sequence $(a_n)$ if and only if,$ i_n = \inf\{a_k : k \geq n\}.$ 
	 			\end{definition}
	 			\begin{definition} If $(a_n)$ is a sequence and $(i_n)$ is defined as above, then
	 			$$\liminf a_n = \lim i_n.$$
	 			\end{definition}

	 			\begin{theorem}
	 				Every limit of subsequences $(a_n)$ is between $\liminf a_n$ and $\limsup a_n.$
	 			\end{theorem}
	 			\begin{proof}
	 				If some subsequence $(a_{m_k})$ converges, it follows that because $(i_n), (s_n)$ are both non-decreasing/non-increasing sequences for all $n,$ $i_n \leq a_n \leq s_n.$ Therefore $i_{n_k} \leq a_{n_k} \leq s_{n_k}.$ Because $(i_n)$ and $(s_n)$ both have limits, then each of their subsequences converge. Then by squeeze theorem we have that $$\liminf a_n \leq \lim a_{n_k} \leq \limsup {a_n}.$$ 
	 			\end{proof}


			\item \textit{Show that a sequence has a limit if its limit supremum and limit infimum are the same.}
				\begin{theorem}
				 	A sequence $(a_n)$ has a limit iff $$\limsup a_n = \liminf a_n = a.$$
				 \end{theorem} 
			 	\begin{proof}
			 	 As above we have that $i_n \leq a_n \leq s_n.$ Since $\lim i_n = \lim s_n = b$, it follows from the squeeze theorem that $\lim a_n = b.$
			 	 On the other hand if $\lim a_n = a,$ we have that every subsequence of $(a_n)$ has a limit, say $b$. Since $\limsup a_n, \liminf a_n$ are limits of subsequences of $a_n$, then they must both be $b.$ This completes the proof.
			 	\end{proof}
			\end{menumerate}

			\newpage
			\setcounter{enumi}{47}
			\item \textit{Deform the treifoil knot in $4$ dimensions.} 



		
		
\end{menumerate}


\end{document}